---
title: "elephants-coord-power-writeup"
author: "Karen Gu"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Power Analysis for Variable Coordination Experiment

Here we simulated further variable coordination experiments with varying numbers of items and participants. Code for the simulations is found in `./elephants-coord-power-analysis.Rmd`. Each simulation is identified by a seed. We define our goal as having any beta coefficient greater than 0, that is, any coordination level besides S implies higher prevalence levels than S alone.

```{r}
calculate.power <- function(results.folder, file.name) {
  read.csv(paste(results.folder, file.name, sep="/")) %>% filter(is.na(group)) %>% mutate(achieved = conditionnp > 0 | conditionpp > 0 | conditionvp > 0)
}

datalist = list()
i <- 0
for (trial in seq(100, 400, 50)) {
  for (item in seq(12, 18, 3)) {
    if (trial == 400) next
    i <- i + 1
    dat <- calculate.power("./results", paste("elephants-coord-sim-", trial, "-items-", item, ".csv", sep=""))
    datalist[[i]] <- dat
  }
}
for (trial in seq(50, 250, 50)) {
  i <- i + 1
  dat <- calculate.power("./results", paste("elephants-coord-sim-", trial, ".csv", sep="")) %>% mutate(n.items = 12)
  datalist[[i]] <- dat
}
for (trial in seq(100, 450, 50)) {
  for (item in seq(15, 21, 3)) {
    i <- i + 1
    file.name <- paste("./results_2", paste("elephants-coord-sim-", trial, "-items-", item, ".csv", sep=""), sep="/")
    if (file.exists(file.name)) {
      dat <- calculate.power("./results_2", paste("elephants-coord-sim-", trial, "-items-", item, ".csv", sep=""))
      datalist[[i]] <- dat
    }
  }
}

power.data <- bind_rows(datalist)
power.data %>% group_by(n.participants,  n.items) %>% count()
```

```{r}
power.data %>% mutate(n.items = factor(n.items)) %>% group_by(n.participants, n.items) %>% summarize(power=mean(achieved)) %>%
  ggplot(aes(x=n.participants, y=power, color=n.items)) +
  geom_line(aes(group=n.items))
```

